Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
done editing Sec. VI

%\AB{Need to add results on the default cluster!}
%
%    \paragraph{Memory-constrained cluster}
    The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
    situation - that is, if the scheduler assumed its memory to be smaller than it actually was and assigned it to a processor
    with not enough memory capacity.
    Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160 for all algorithm variants
    ended with a valid makespan without recomputation.
    In case of \heft, $14$ valid initial makespans were computed.
    Out of them, $13$ managed to stay valid until the end, after all the update requests.
    The same $13$ experiments ended with a valid makespan in case of no recomputation.
    So, these workflows required so few resources that there was no point in re-scheduling them.
    %$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
    %rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
    %only, the success rate of not recomputing is $92\%$.
    In case of \heftmm, all $290$ workflows could be scheduled initially and all the schedules remained valid until the end.
    $16$ experiments ended with a successful makespan without recomputation.
    The rate of successful schedules without recomputation is therefore~$5.5\%$.
    \heftblc could produce $142$ valid initial schedules and kept $141$ of them valid until the end.
    $50$ experiments were successful without recomputation, too, making it $35\%$ out of all successful final schedules.
    \heftbl kept $105$ schedules valid until the end out of $110$ initial valid schedules.
    $55$ were able to be kept valid until the end even without recomputation, roughly $50\%$ of all successes.

    \heftbl and \heftblc were successful on smaller workflows and failed on larger ones, the success of the strategy without
    recomputation was limited to even the smallest of these smaller workflows.
    So, the strategy without recomputation delivered valid makespans (independently of the algorithm) on $56$ original
    workflows with $<100$ tasks, $47$ 200-task ones, $25$ 1000-task ones and $6$ 2000-task ones.

    Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
    With growing size of the workflow, the excess makespan of not recomputing grows - from $13.9\%$ to $20\%$ for \heftbl,
    from $12.7\%$ to $18.7\%$ on \heftblc (but there is no data for the 2000-task workflows in this case),
    $12.1\%$ to $23.5\%$ for \heftmm.
    The larger variations for \heft can be explained by the small amount of data -- for instance, there were only 2 200-task
    workflows for this case.

@@

\subsection{Running times of the heuristics}
\label{sec.expe.t}

    To be able to answer the runtime system without holding it up for too long, the scheduler needs to 
    be able to compute a schedule rapidly. %provide a fast answer.
    The bottom-level-based heuristics \heftbl and \heftblc provide smaller running times than \heftmm, 
    and also scale better with growing workflow
    sizes~(see Fig.~\ref{fig:runtimes-log}).
    Their running times are similar and grow from tens of milliseconds for the smallest workflows to $25-27$ seconds 
    for the largest workflows.
    \heftmm, however, needs to compute a memory-optimal traversal of the entire workflow to compute the ranks 
    of the tasks,
    so its running time scales from also tens of milliseconds for the smallest workflows, 
    to thousands of seconds - $1172.7$ for \numprint{20000}-task workflows and
    $2994.9$ seconds for the largest, \numprint{30000}-task workflows.
    This increased running time is, though, offset by the unique $100\%$ success rate this algorithm 
    obtained when scheduling large
    workflows in difficult (memory-constrained) setups.

@@

\section{Conclusion} %  \skug{Full: 0, Polished: 0}}
\label{sec:conc}

>>>>

%\AB{Need to add results on the default cluster!}
%
%    \paragraph{Memory-constrained cluster}
The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160 
for all algorithm variants end with a valid makespan without recomputation.
In case of \heft, $14$ valid initial makespans were computed.
Out of them, $13$ remain valid until the end, after all the update requests.
The same $13$ experiments end with a valid makespan in case of no recomputation.
So, these workflows require so few resources that there is no point in re-scheduling them.
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.
In case of \heftmm, all $290$ workflows can be scheduled initially and all the schedules remain valid until the end.
$16$ experiments end with a successful schedule without recomputation, a rate of~$5.5\%$.
\heftblc produces $142$ valid initial schedules and keeps $141$ of them valid until the end.
$50$ experiments are successful without recomputation, a rate of $35\%$ out of all successful final schedules.
\heftbl keeps $105$ schedules valid until the end out of $110$ initial valid schedules.
$55$ remain valid until the end even without recomputation, roughly $50\%$ of all successes.

\heftbl and \heftblc are successful on smaller workflows and fail on larger ones, 
the success of the strategy without recomputation is limited to even the smallest of these smaller workflows.
Thus, the strategy without recomputation delivers valid makespans (independently of the algorithm) 
on $56$ original workflows with $<100$ tasks, $47$ $200$-task ones, $25$ $1000$-task ones, and $6$ $2000$-task ones.

Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
With growing size of the workflow, the excess makespan of not recomputing grows -- from $13.9\%$ to $20\%$ for \heftbl,
from $12.7\%$ to $18.7\%$ on \heftblc (but there is no data for the $2000$-task workflows in this case), % TODO: why not?
$12.1\%$ to $23.5\%$ for \heftmm.
The larger variations for \heft can be explained by the small amount of data -- for instance, there are
only $2$ $200$-task workflows for this case.

@@

\subsection{Running times of the heuristics}
\label{sec.expe.t}
%
In order to answer the runtime system without holding it up for too long, the scheduler needs to 
compute a schedule reasonably quickly. %provide a fast answer.
The bottom-level-based heuristics \heftbl and \heftblc yield smaller running times than \heftmm, 
and also scale better with growing workflow sizes~(see Fig.~\ref{fig:runtimes-log}).
Their running times are similar and grow from tens of milliseconds for the smallest workflows to 
$25$-$27$ seconds for the largest workflows.
\heftmm, in turn, computes a memory-optimal traversal of the entire workflow to compute the task ranks. 
It also takes only tens of milliseconds for the smallest inputs, but requires
thousands of seconds for the large(st) workflows ($1172.7$s for \numprint{20000}-task workflows and
$2994.9$s for \numprint{30000}-task ones).
This increased running time is, however, offset by the unique $100\%$ success rate this algorithm 
obtained in our experiments when scheduling large workflows in difficult (memory-constrained) setups.

@@

\section{Conclusion}
\label{sec:conc}
